---
title: "Exponential distribution simulation"
author: "Ricardo Schifini"
date: "May 3, 2019"
output: html_document
---
# The Exponential Distribution

The exponential distribution is used to describe the time between independent events that happen at an average rate.

This distribution can be easily deduced analitycaly, but it can be also simulated by using an uniform probability distribution.

## Simulating the Exponential Distribution

Independent events that happen at an average rate can be simulated with the Monte Carlo method and a uniform distribution.

Events that happen at an average rate of `R` events/time_unit can be simulated by a total of `T * R` events, where `T` is the total time units.

### Parameters

`R` is the average rate of the events
`t` is the simulation's total time

```{r}
R = 5
t = 1000000
```

### Events

This means that we have to create `R*T` events having a random time of happening uniformly distributed between 0 and `T`

```{r}
events = runif(R*t ,0, t)
```
We need to calculate the time between consecutive events. To do so, we first need to sort the events from low to high.

```{r}
t_events = diff(sort(events))

```

### Graphs

Probability distribution

```{r}
j = hist(t_events, 500, plot = F)
plot(j$breaks[-1],j$counts, type = "l")

```

Cumulative distribution

```{r}
x = sort(t_events)
y = (1:length(t_events))/length(t_events)
sel = seq(from=1, along.with = x, by = 100)

plot(x[sel], y[sel], type = "l")

z = rexp(t, R)

xe = sort(z)
ye = (1:length(z))/length(z)
sel = seq(from=1, along.with = xe, by = 100)

points(xe[sel], ye[sel], col='red')

```
